DRAFT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- DRAFT

### 2024-03-22 docs/_tex/index.tex
pierre's comments

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing, Seagrass, Coastal
Ecosystems, Neural Network},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{PREPRINT -- Discriminating Seagrasses From Green Macroalgae in
European Intertidal areas using high resolution multispectral drone
imagery -- PREPRINT.}
\author[1]{Simon Oiry%
\corref{cor1}%
}
 \ead{oirysimon@gmail.com} 
\author[1]{Bede Ffinian Rowe Davies%
%
}

@@

\includegraphics[width=6.63in,height=\textheight]{Figures/table_validation_px.png}

@@

@@

The primary objective of this study was to develop a method for the
accurate classification of macrophytes on intertidal mudflats,
specifically focusing on distinguishing between Chlorophyceae (green
macroalgae) and marine Magnoliopsida (seagrasses) using multispectral
drone data. The ability to differentiate between various types of
vegetation, as demonstrated in this study, plays a critical role in
ecological monitoring and coastal management. By distinguishing between
seagrasses and macroalgae, our approach facilitates targeted
conservation strategies, enabling more effective preservation and
restoration efforts in coastal ecosystems. The discrimination of
seagrasses from green macroalgae presents significant challenges
\citetext{\citealp[ ]{oiry2021using}; \citealp[
]{bannari2022}; \citealp{veettil2020opportunities}}, primarily due to
the similarities on their spectal signatures in the visible region of
the eletromagnetic spectra due to shared pigment
, Figure~\ref{fig-Pigm}, but also by the frequent spatial mixing of
these macrophytes. Besides chlorophyll-a that is common to all
vegetation types, these two green macrophytes have in common other
photosynthetic pigments such as chlorophyll-b, and accessory carotenoid
pigments such as zeaxantin, lutein and neoxanthin
(Figure~\ref{fig-Pigm}). This spectral overlap is further complicated by
the intermingling of seagrasses and green macroalgae in the same spatial
locations, posing a significant challenge for remote sensing aimed at
accurately mapping and monitoring coastal ecosystems. Our study
addresses these complexities by using high-resolution drone imagery with
10 spectral bands. \citep{Davies2023} have shown that having at least
eight spectral bands ranging between 500 nm to 850 nm including a green
band at 530 nm and another one in the RedEdge region at 730 nm was
crucial to accurately discriminate amoung green macrophytes.

@@

The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
identified that the band at 531 nm was the most important one for
accurately identifying Chlorophyceae. In fact, at this wavelength,
Chlorophyceae exhibited the highest reflectance (raw and standardised)
among all other classes, highlighting the difference in accessory
pigments (i.e.~carotenoid) between seagrasses and green macroalgae
\citep{repolho2017seagrass}.

@@

\subsection{Spectral Spatial Temporal Resolution impact on the
prediction}\label{spectral-spatial-temporal-resolution-impact-on-the-prediction}

@@

With the increase in nutrient concentrations in coastal waters,
macroalgal blooms are becoming increasingly common in many regions
around the world \citetext{\citealp[
]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
negative impacts on local economic activities, including human health,
fishing and aquaculture, tourism, and recreational activities
\citetext{\citealp[ ]{villares1999nitrogen}; \citealp{ye2011green}}. The
first green tide events (i.e.~bloom of green macroalgae of the genus
\emph{Ulva}) were reported in Brittany, France, back in the 1970s and
have since been a concern for local policies and economic activities
\citep{menesguen2018marees}. Some regions of the world have witnessed an
increase in brown macroalgae blooms, predominantly involving algae of
the genus \emph{Sargassum} \citep{louime2017sargassum}. Satellite remote
sensing has proven to be a valuable tool for mapping the spatial and
temporal extent of macroalgal blooms worldwide. However, due to its
limitations in spatial resolution, it can only effectively map
well-developed blooms \citetext{\citealp[
]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
drone imagery, coupled with an accurate classification algorithm, could
be utilized to map the early stages of macroalgal blooms in areas known
to have regular blooms or in new sites. Indeed, this approach could
provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is
time and resource-intensive, and the findings are often difficult to
up-scale. Earth observation methods can bridge this gap and meet the
needs for monitoring coastal ecosystems
\citep{papathanasopoulou2019satellite}. The retrieval of Essential
Biodiversity Variables and Essential Ocean Variables through satellite
observations is increasingly common, enabling comprehensive monitoring
of entire ecosystems over extended time periods \citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
significance of monitoring the coastal environment, particularly in
light of the Water Framework Directive (WFD ; \citep{WFD2000}), cannot
be overstated in environmental management and conservation efforts. The
WFD mandates the achievement and maintenance of ``good ecological
status'' for all European waters, which necessitates a comprehensive
understanding and monitoring of aquatic ecosystems, including coastal
habitats like seagrass beds \citetext{\citealp[
]{foden2007angiosperms}; \citealp[
]{nordlund2024one}; \citealp{Zoffoli2021}}.

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={DRAFT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- DRAFT},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing, Seagrass, Coastal
Ecosystems, Neural Network},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{DRAFT -- Discriminating Seagrasses From Green Macroalgae in
European Intertidal areas using high resolution multispectral drone
imagery -- DRAFT}
\author[1]{Simon Oiry%
\corref{cor1}%
}
 \ead{oirysimon@gmail.com} 
\author[1]{Bede Ffinian Rowe Davies%
%
}

@@

\includegraphics[width=6.63in,height=\textheight]{Figures/High_res/table_validation_px.png}

@@

The primary objective of this study was to develop a method for the
accurate classification of macrophytes on intertidal mudflats,
specifically focusing on distinguishing between Chlorophyceae (green
macroalgae) and marine Magnoliopsida (seagrasses) using multispectral
drone data. The ability to differentiate between various types of
vegetation, as demonstrated in this study, plays a critical role in
ecological monitoring and coastal management. By distinguishing between
seagrasses and macroalgae, our approach facilitates targeted
conservation strategies, enabling more effective preservation and
restoration efforts in coastal ecosystems. The discrimination of
seagrasses from green macroalgae presents significant challenges
\citetext{\citealp[ ]{oiry2021using}; \citealp[
]{bannari2022}; \citealp{veettil2020opportunities}}, primarily due to
the similarities on their spectal signatures in the visible region of
the eletromagnetic spectra due to shared pigment
, Figure~\ref{fig-Pigm}, but also by the frequent spatial mixing of
these macrophytes. Besides chlorophyll-a that is common to all
vegetation types, these two green macrophytes have in common other
photosynthetic pigments such as chlorophyll-b, and accessory carotenoid
pigments such as zeaxantin, lutein and neoxanthin
(Figure~\ref{fig-Pigm}).

@@

This spectral overlap is further complicated by the intermingling of
seagrasses and green macroalgae in the same spatial locations, posing a
significant challenge for remote sensing aimed at accurately mapping and
monitoring coastal ecosystems. Our study addresses these complexities by
using high-resolution drone imagery with 10 spectral bands.
\citep{Davies2023} have shown that having at least eight spectral bands
ranging between 500 nm to 850 nm including a green band at 530 nm and
another one in the RedEdge region at 730 nm was crucial to accurately
discriminate amoung green macrophytes.

@@

The VIP analysis of the Neural Network model (Figure~\ref{fig-VIP})
identified that the band at 531 nm was the most important one for
accurately identifying Chlorophyceae. In fact, at this wavelength,
Chlorophyceae exhibited the highest reflectance (raw and standardised)
among all other classes, highlighting the potential differences in
accessory pigment ratios (i.e.~carotenoid) between seagrasses and green
macroalgae \citep{repolho2017seagrass}.

@@

\subsection{Impact of Spectral, Spatial, and Temporal Resolution on
Predictive
Accuracy}\label{impact-of-spectral-spatial-and-temporal-resolution-on-predictive-accuracy}

@@

With the increase in nutrient concentrations in coastal waters,
macroalgal blooms are becoming increasingly common in many regions
around the world \citetext{\citealp[
]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
negative impacts on local economic activities, including human health,
fishing and aquaculture, tourism, and recreational activities
\citetext{\citealp[ ]{villares1999nitrogen}; \citealp{ye2011green}}. The
first green tide events (i.e.~bloom of green macroalgae of the genus
\emph{Ulva}) were reported in Brittany, France, back in the 1970s and
have since been a concern for local policies and economic activities
\citep{menesguen2018marees}. Some regions of the world have witnessed an
increase in brown macroalgae blooms, predominantly involving algae of
the genus \emph{Sargassum} \citep{louime2017sargassum}. Satellite remote
sensing has proven to be a valuable tool for mapping the spatial and
temporal extent of macroalgal blooms worldwide. However, due to its
limitations in spatial resolution, it can only effectively map
well-developed blooms \citetext{\citealp[ ]{rs13081408}; \citealp[
]{klemas2012remote}; \citealp{HARO2023103451}}. High spatial resolution
drone imagery, coupled with an accurate classification algorithm, could
be utilized to map the early stages of macroalgal blooms in areas known
to have regular blooms or in new sites. Indeed, this approach could
provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is
time and resource-intensive, and the findings are often difficult to
up-scale. Earth observation methods can bridge this gap and meet the
needs for monitoring coastal ecosystems
\citep{papathanasopoulou2019satellite}. The retrieval of Essential
Biodiversity Variables and Essential Ocean Variables through satellite
observations is increasingly common, enabling comprehensive monitoring
of entire ecosystems over extended time periods \citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The Water
Framework Directive \citep[WFD :][]{WFD2000} mandates the achievement
and maintenance of ``good ecological status'' for all European waters,
which necessitates a comprehensive understanding and monitoring of
aquatic ecosystems, including coastal habitats like seagrass beds
\citetext{\citealp[ ]{foden2007angiosperms}; \citealp[
]{nordlund2024one}; \citealp{Zoffoli2021}}.

### 2024-03-22 index.qmd
pierre's comments

title: PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

@@

gaf<-rast(list(gaf_low_multi,Gafanha_low_pred)) %>% 
  as.data.frame(xy = F) %>% 
  dtplyr::lazy_dt() %>% 
  dplyr::filter(B1 != 65535,
                pred != 0) %>%
  as_tibble() %>% 
  rename(Class = "pred") %>%
  mutate(pxl_ID = c(1:nrow(.))) %>% 
  pivot_longer(-c(Class,pxl_ID), names_to = "band",values_to = "value") %>% 
  left_join(micasense, by = c("band" = "Band_ID")) %>% 
  group_by(Class, Wavelength) %>% 
  dplyr::summarise(mean = mean(value),
                   sd = sd(value),
                   max = max(value),
                   min = min(value),
                   median = median(value)) %>%  
  mutate(Class = case_when(Class == 1 ~ "Bare Sediment",
                              Class == 2 ~ "D - Chloropyceae",
                              Class == 3 ~ "Bare Sediment",
                              Class == 4 ~ "A - MagnoliopsidaL",
                              Class == 5 ~ "E - Microphytobenthos",
                              Class == 6 ~ "A - Magnoliopsida",
                              Class == 7 ~ "B - Phaeophyceae",
                              Class == 8 ~ "C - Rhodophyceae",
                              Class == 9 ~ "Sun Glint",
                              Class == 10 ~ "Water",
                              Class == 11 ~ "Xanthophyceae",
                              TRUE ~ "NA"))

@@

save_as_image(flx2, "Figures/table_validation_px.png", res = 300)

@@

knitr::include_graphics("Figures/table_validation_px.png")
```

@@

@@

y_axis_text_pigment<-data.frame(x = rep(-0.05,5),
                                y = c(0.5,1.5,2.5,3.5,4.5), 
                                lab = c("Rhodophyceae",
                                    "Phaeophyceae",
                                    "Bacillariophy.",
                                    "Chlorophyceae",
                                    "Magnoliopsida")
                                )
x_axis_text_pigment<-data.frame(y = rep(5.5,9),
                                x = c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5),
                                lab = c("Chlb","Chlc","Fuco","Zea","Diad","Lut","Neo","PE","PC")
                                )

@@

ggsave("./Figures/Disc_Pigment_Table.png",rast_pigment, width= 1066*4, height=516*4, units = "px")

@@

The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data. The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and coastal management. By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems. The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes. Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm). This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands. @Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate amoung green macrophytes.

@@

The VIP analysis of the Neural Network model (@fig-VIP) identified that the band at 531 nm was the most important one for accurately identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the difference in accessory pigments (i.e. carotenoid) between seagrasses and green macroalgae [@repolho2017seagrass].

@@

## Spectral Spatial Temporal Resolution impact on the prediction

@@

With the increase in nutrient concentrations in coastal waters, macroalgal blooms are becoming increasingly common in many regions around the world  [@sutton2011european ; @ye2011green]. These blooms can have negative impacts on local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green]. The first green tide events (i.e. bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees]. Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum]. Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide. However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote]. High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites. Indeed, this approach could provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020]. The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts. The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].

>>>>

title: DRAFT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- DRAFT

@@

gaf<-rast(list(gaf_low_multi,Gafanha_low_pred)) %>% 
  as.data.frame(xy = F) %>% 
  dtplyr::lazy_dt() %>% 
  dplyr::filter(B1 != 65535,
                pred != 0) %>%
  as_tibble() %>% 
  rename(Class = "pred") %>%
  mutate(pxl_ID = c(1:nrow(.))) %>% 
  pivot_longer(-c(Class,pxl_ID), names_to = "band",values_to = "value") %>% 
  left_join(micasense, by = c("band" = "Band_ID")) %>% 
  group_by(Class, Wavelength) %>% 
  dplyr::summarise(mean = mean(value),
                   sd = sd(value),
                   max = max(value),
                   min = min(value),
                   median = median(value)) %>%  
  mutate(Class = case_when(Class == 1 ~ "Bare Sediment",
                              Class == 2 ~ "D - Chlorophyceae",
                              Class == 3 ~ "Bare Sediment",
                              Class == 4 ~ "A - MagnoliopsidaL",
                              Class == 5 ~ "E - Microphytobenthos",
                              Class == 6 ~ "A - Magnoliopsida",
                              Class == 7 ~ "B - Phaeophyceae",
                              Class == 8 ~ "C - Rhodophyceae",
                              Class == 9 ~ "Sun Glint",
                              Class == 10 ~ "Water",
                              Class == 11 ~ "Xanthophyceae",
                              TRUE ~ "NA"))

@@

save_as_image(flx2, "Figures/High_res/table_validation_px.png", res = 300)

@@

knitr::include_graphics("Figures/High_res/table_validation_px.png")
```

@@

The primary objective of this study was to develop a method for the accurate classification of macrophytes on intertidal mudflats, specifically focusing on distinguishing between Chlorophyceae (green macroalgae) and marine Magnoliopsida (seagrasses) using multispectral drone data. The ability to differentiate between various types of vegetation, as demonstrated in this study, plays a critical role in ecological monitoring and coastal management. By distinguishing between seagrasses and macroalgae, our approach facilitates targeted conservation strategies, enabling more effective preservation and restoration efforts in coastal ecosystems. The discrimination of seagrasses from green macroalgae presents significant challenges [@oiry2021using ; @bannari2022 ; @veettil2020opportunities], primarily due to the similarities on their spectal signatures in the visible region of the eletromagnetic spectra due to shared pigment [@mckenzie2020global ; @fig-Pigm], but also by the frequent spatial mixing of these macrophytes. Besides chlorophyll-a that is common to all vegetation types, these two green macrophytes have in common other photosynthetic pigments such as chlorophyll-b, and accessory carotenoid pigments such as zeaxantin, lutein and neoxanthin (@fig-Pigm).

@@

y_axis_text_pigment<-data.frame(x = rep(-0.05,5),
                                y = c(0.5,1.5,2.5,3.5,4.5), 
                                lab = c("Rhodophyceae",
                                    "Phaeophyceae",
                                    "Bacillariophy.",
                                    "Chlorophyceae",
                                    "Magnoliopsida")
                                )
x_axis_text_pigment<-data.frame(y = rep(5.5,9),
                                x = c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5),
                                lab = c("Chl-b","Chl-c","Fuco","Zea","Diad","Lut","Neo","PE","PC")
                                )

@@

ggsave("./Figures/High_res/Disc_Pigment_Table.png",rast_pigment, width= 1066*4, height=516*4, units = "px")

@@

This spectral overlap is further complicated by the intermingling of seagrasses and green macroalgae in the same spatial locations, posing a significant challenge for remote sensing aimed at accurately mapping and monitoring coastal ecosystems. Our study addresses these complexities by using high-resolution drone imagery with 10 spectral bands. @Davies2023 have shown that having at least eight spectral bands ranging between 500 nm to 850 nm including a green band at 530 nm and another one in the RedEdge region at 730 nm was crucial to accurately discriminate amoung green macrophytes.

@@

The VIP analysis of the Neural Network model (@fig-VIP) identified that the band at 531 nm was the most important one for accurately identifying Chlorophyceae. In fact, at this wavelength, Chlorophyceae exhibited the highest reflectance (raw and standardised) among all other classes, highlighting the potential differences in accessory pigment ratios (i.e. carotenoid) between seagrasses and green macroalgae [@repolho2017seagrass].

@@

## Impact of Spectral, Spatial, and Temporal Resolution on Predictive Accuracy

@@

With the increase in nutrient concentrations in coastal waters, macroalgal blooms are becoming increasingly common in many regions around the world  [@sutton2011european ; @ye2011green]. These blooms can have negative impacts on local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green]. The first green tide events (i.e. bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees]. Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum]. Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide. However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote ; @HARO2023103451]. High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites. Indeed, this approach could provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020]. The Water Framework Directive [WFD : @WFD2000] mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
